\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2016-11-30 Response.tex

\item \textit{If the inertia matrix is unknown, how to modify the suggested control system guaranteeing the asymptotic stability?}
Even with an uncertainty in the inertia matrix, one could redefine the system and treat this as an unknonw external disturbance instead.

Show the algebra that allows for either a multiplicative or additive uncertainty in the inertia matrix as equivalent to an external torque

\item \textit{The state inequality constraint is not violated based on adding the repulsive term in the attitude error function. Is this result still valid if this constraint becomes time-dependent?}

We're focused on the stationary obstacle in this manuscript. 
We are considering the addition of a time-varying obstacle in a future research

@@

\item \textit{Specification of the sensors in the experiments should be included in the manuscript.}

Additional detail on the sensors and their operation has been included:
\begin{correction}
    Attitude information is measured by a combination of both on and off board sensor systems.
    The VectorNav VN-100 is a rugged, miniature high-performance inertial measurement unit which provides high frequency angular velocity measurements.
    A Vicon motion capture system is installed within the test environment and used to provide high accuracy attitude measurements. 
    A series of reflective markers are placed on the hexrotor and their relative position is captured by a series of infrared optical cameras. 
    Assuming a fixed rigid body, the Vicon system is able to derive the attitude of the hexrotor and transmit this data to the processor onboard the hexrotor.
    The control input is computed on-board, using the full state measurement, and implemented at approximately \SI{100}{\hertz}.
\end{correction}
\end{enumerate}

\subsection*{Reviewer 5}
\textit{This paper studies adaptive control design for the attitude dynamics of a rigid body system with state inequality constraints. The designed controller is proved to be asymptotically stabilized and may enable attitude stabilization in the presence of unknown disturbances. The attitude trajectory by the controller may avoid undesired regions. The effectiveness of the proposed control system is demonstrated through numerical simulations and experimental results. This paper is well written and the research contents are interesting. The main contributions of this paper are the new geometric adaptive control system proposed by the authors and its experimental verification. This paper is well organized and almost need not to make any changes. This reviewer suggests that it can be accepted for publication in International Journal of Control, Automation and Systems.}

\begin{enumerate}
\item \textit{The only question is that all the figures in this paper are too small and are not legible. The meanings of different lines in one figure should be explained in the title content.}

All of the figures have been enlarged and modified to span the entire page rather than a single column. 
In addition, the captions of~\cref{fig:config_error,fig:adapt,fig:con} have been modified to mention the fact that they are plotting the components of a vector in a single plot or using a subplot.
\end{enumerate}

### 2016-11-30 Response.tex

\subsection*{Reviewer 3}

\textit{This paper considers the attitude control with inequality constraints. Attitude dynamics with matched uncertainty which is parameterized by a unknown constant matrix, and hard constants expressed by rotation matrix are considered. Although the problem is very interesting, the proofs for major results on the case with plant uncertainty are far from complete. Some comments are listed below.}

\begin{enumerate}
\item \textit{Please give a precise definition of variation used in the paper, e.g., eq. (17) and (18)}
The variation of the rotation matrix is defined as
\begin{align*}
    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
\end{align*}
We have augmented the proof of Proposition 1, which is given in Appendix 1, to include the definition of the variation as:
\begin{correction}
The infinitesimal variation of a rotation matrix is defined as
\begin{align*}
    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
\end{align*}
\end{correction}

\item \textit{This is serious. In section 2, the upper bounds listed in Proposition 4 are given. Well, these should be the properties that your controller guarantees not come from the set D you've defined. Since these properties are used to derive the bound H which is used to derive the result in Proposition 5, the stability proof under the proposed controller is far from complete.}

Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
The details in~\cref{proof:att_control,proof:eR_dot_bound} are valid in the selected domain \( D \) about the desired attitude.
Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.

The set \( D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists a \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e. the desired attitude should be sufficiently far away from the constraints. 
We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).

{\Large Add an excerpt of a similar discussion in the manuscript}

\item \textit{Typo in eq. (40).}

### 2016-12-05 Response.tex

\item \textit{ In general, the external disturbance is a time-varying signal even though it is bounded. Thus, authors should consider the time-varying disturbance case.}

It is true that in general, the external disturbances on a system will be time varying.
However, the form of uncertainty shown in \( (1) \) is commonly used in the adaptive control literature~\cite{lee2013b,ioannou2012}.
As a result, we use this same form of uncertainty, namely that the uncertain disturbance is additive in nature and enters through the input channel.
In addition, a wide variety of disturbances is accurately represented by this formulation in the aerospace engineering field and several examples are given in the article.
Furthermore, it has been shown in~\cite{ioannou2012} that this form of adaptive control is able to handle time-varying uncertainties in which the uncertain term is varying sufficiently slowly as compared to the controlled dynamics.

How slowly do the uncertainties have to behave for the simulation?

\item \textit{If the inertia matrix is unknown, how to modify the suggested control system guaranteeing the asymptotic stability?}

In this work, we are focused on the design of attitude controllers in the presence of state constraints. 
The addition of an adaptive update law allows the system to stabilize in the presence of unknown external disturbances.
We are not considering the case of an unknown inertia matrix, but rather assume that there exists accurate knowledge of the rigid body. 
This assumption is relatively simple to satisfy as any physical control system will first have an accurate model of the system itself.
For example, the mass and inertia properties of all spacecraft are accurately measured and verified prior to launch.

In addition, the uncertainty model presented in the paper is commonly used in the adaptive control literature.
Also, it is possible to represent a uncertain or varying inertia matrix as an external disturbance torque. 
For example, Euler's law gives the relationship for the rate of change of angular momentum
\begin{align*}
    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
\end{align*}
Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment. 
In this manner, it is possible to represent a wide array of possible forms of system uncertainty.

### 2016-12-05 Response.tex

In this work, we are focused on the design of attitude controllers in the presence of state constraints. 
The addition of an adaptive update law allows the system to stabilize in the presence of unknown external disturbances.
We are not considering the case of an unknown inertia matrix, but rather assume that there exists accurate knowledge of the rigid body. 
This assumption is relatively simple to satisfy as any physical control system will first have an accurate model of the system itself.
For example, the mass and inertia properties of all spacecraft are accurately measured and verified prior to launch.

In addition, the uncertainty model presented in the paper is commonly used in the adaptive control literature.
Also, it is possible to represent a uncertain or varying inertia matrix as an external disturbance torque. 
For example, Euler's law gives the relationship for the rate of change of angular momentum
\begin{align*}
    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
\end{align*}
Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment. 
In this manner, it is possible to represent a wide array of possible forms of system uncertainty.

\item \textit{The state inequality constraint is not violated based on adding the repulsive term in the attitude error function. Is this result still valid if this constraint becomes time-dependent?}

In this work, we are specifically concerned with presenting a geometric attitude controller on \( \SO \) in the presence of state inequality constraints.
More specifically, we are assuming that these constraints are time-invariant rather than time dependent. 
This type of constraint is representative of the attitude constraints that are frequently experienced in the attitude control of spacecraft. 
For example, various keep-out zones for sensitive electro-optical sensors are well represented as a fixed constraint in the inertial frame. 
In addition, the time scale of the attitude dynamics, and therefore any attitude control maneuver, is much shorter than the time scale of the translational dynamics.
In other words, a time-dependent constraint in the inertial frame will evolve at a much slower rate as compared to the attitude dynamics. 
As a result, it is possible to model the time-varying constraints as a series of time-invariant constraints in the inertial frame. 
In this situation, the presented approach allows for a straightforward method to design an attitude stabilization control law. 
However, this is a very applicable suggestion and it is an area of current research efforts.

### 2016-12-05 Response.tex

\textit{This paper considers the attitude control with inequality constraints. Attitude dynamics with matched uncertainty which is parameterized by a unknown constant matrix, and hard constants expressed by rotation matrix are considered. Although the problem is very interesting, the proofs for major results on the case with plant uncertainty are far from complete. Some comments are listed below.}

\begin{enumerate}
\item \textit{Please give a precise definition of variation used in the paper, e.g., eq. (17) and (18)}
The variation of the rotation matrix is defined as
\begin{align*}
    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
\end{align*}
We have augmented the proof of Proposition 1, which is given in Appendix 1, to include the definition of the variation as:
\begin{correction}
The infinitesimal variation of a rotation matrix is defined as
\begin{align*}
    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
\end{align*}
\end{correction}

\item \textit{This is serious. In section 2, the upper bounds listed in Proposition 4 are given. Well, these should be the properties that your controller guarantees not come from the set D you've defined. Since these properties are used to derive the bound H which is used to derive the result in Proposition 5, the stability proof under the proposed controller is far from complete.}

Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
The presented details, which are shown in~\cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.

The set \( D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e. the desired attitude should be sufficiently far away from the constraints. 
We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
Therefore, the given domain \( D \) is an open neighborhood of the desired attitude configuration, \(R_d\), and the Lyapunov stability results are valid in this domain.

The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
In general, this is not a difficult assumption to satisfy as the desired attitude will typically be located far from the constrained regions.
We have augmented the manuscript with some additional discussion of the chosen domain \( D \) in~\Cref{proof:eR_dot_bound}.

\begin{correction}
    We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
    Furthermore, we can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
\end{correction}
\item \textit{Typo in eq. (40).}

### 2016-12-05 manuscript.tex
Reviewer 3 #2 response
Add more detail about the open neighborhood properties of the domain D

\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
%	We know that \( B \to \infty \) as the constraint is neared. 
%	We assume that \( B > \psi \) which implies that \( A < 1 \).
%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.

>>>>

\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
%	We know that \( B \to \infty \) as the constraint is neared. 
%	We assume that \( B > \psi \) which implies that \( A < 1 \).
%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
Furthermore, we can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
Therefore, the selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
